Object detection for Verification Based Annotation

### 2019-11-27 paper.tex
Updates from Overleaf

\usepackage{hyperref}
\usepackage{multirow}
\newcommand{\STAB}[1]{\begin{tabular}{@{}c@{}}#1\end{tabular}}

@@

@@

@@

Code for this paper can be found \href{https://github.com/saulzar/detection/tree/thesis}{link}, under the tag ``thesis'', with details surrounding the cropping procedure, default training and augmentation parameters etc.

@@

A selection of the datasets with images and annotations (as well as annotation history logs) can be found at \href{http://academictorrents.com/details/e780e1a9e898e53e72c16cb5fcc6d61d90cc4d27}{link}.

@@

\begin{figure}[htb] 
  \centering
  \includegraphics[width=1.0\linewidth]{figures/splits_scatters.pdf}
  \caption{Comparison of different inference methods across one training run with inference using tiling vs. Inference on full images. Training occurs on crops and evaluating on full images. }   
  \label{fig:inference_method}
\end{figure}

>>>>

% \usepackage{hyperref}
\usepackage{multirow}
\newcommand{\STAB}[1]{\begin{tabular}{@{}c@{}}#1\end{tabular}}

@@

\IEEEoverridecommandlockouts
\IEEEpubid{\makebox[\columnwidth]{978-1-7281-4187-9/19/\$31.0\textcopyright{}2019 IEEE \hfill}
\hspace{\columnsep}\makebox[\columnwidth]{ }}

@@

\IEEEpubidadjcol

@@

% Code for this paper can be found \href{https://github.com/saulzar/detection/tree/thesis}{link}, under the tag ``thesis'', with details surrounding the cropping procedure, default training and augmentation parameters etc.

@@

% A selection of the datasets with images and annotations (as well as annotation history logs) can be found at \href{http://academictorrents.com/details/e780e1a9e898e53e72c16cb5fcc6d61d90cc4d27}{link}.

@@

\begin{figure}[htb] 
  \centering
  \includegraphics[width=1.0\linewidth]{figures/splits_scatters.pdf}
  \caption{Comparison of different inference methods across one training run inference using tiling vs. inference on full images. Training occurs on crops and evaluating on full images. }   
  \label{fig:inference_method}
\end{figure}
